Untitled

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
working on discussion

<!-- As modelling methods have become more sophisticated, some have argued that more complex models are required to adequately explore certain types of public health topics [@SQUIRES2016588].  -->
<!-- Accountability for both the scientific quality and social acceptability of health economic models can be improved.  -->
<!-- Modellers should be faithful to reaity and values of users DOI: 10.1002/asi.23697 -->

@@

<!-- [https://doi.org/10.1017/S026646232200321X].  -->

Health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017]. Funding for health economic modelling projects rarely extend to provision of medium term support for model updates and improvements. The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.
<!-- Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year.A model can grow stale when changes in the real world, whether sudden (e.g. new pandemics) or gradual (e.g. demographic), is not represented by corresponding updates to relevant model features. Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation.  -->

A potential strategy for improving model accountability, reusability and updatability is to make models both modular and open-source.
<!-- Modularity -->
<!-- Definition, value - Computational biology https://doi.org/10.1371/journal.pcbi.1009513 -->
<!-- reusable, interoperable, trans- parent and able to accommodate updates to both data and algorithms - Ecology DOI: 10.1111/2041-210X.14034 -->
<!-- Brain OS modularity: https://www.frontiersin.org/articles/10.3389/fninf.2022.883223/pdf -->

@@

<!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
Modular models provide an opportunity for multiple modelling teams to contribute to, test and reuse models. To enhance this capacity, modular models may be implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust]. Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs)  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].

<!-- Open source is more than open access (limited discussion). -->
<!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->

<!-- and for mental health specifically [@Occhipinti2021],  -->
<!-- could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context. Dynamic systems methods might provide the foundations for developing   -->
<!-- and models designed for multiple purposes r -->

@@

<!-- that rarely explores complex dynamic systems  -->
<!-- [PECUNIA] -->

<!-- Mental health economic studies predominantly examine the affordability and value for money of individual programs [@RN34]. Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].  -->

 <!-- as part of the Open Value Initiative [@Jansen2019].  -->

<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.  -->
 <!-- but, as with health economics more generally, OSHEMs remain rare. Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models. -->

<!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." -->

 <!-- http://hdl.handle.net/1893/27205-->

>>>>

@@

Health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017]. Funding for health economic modelling projects rarely extend to provision of medium term support for model updates and improvements. The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.

A potential strategy for improving model accountability, reusability and updatability is to make models both modular and open-source.

@@

Modular models provide an opportunity for multiple modelling teams to contribute to, test and reuse models. To enhance this capacity, modular models may be implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust]. Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs)  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].

@@

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
working on discussion

---
title: "Untitled"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r checktb, tab.cap='TIMELY Checklist applied to utility mapping study', tab.id = 'checktb', echo = F, results = 'asis'}
    #  a <- c("TEST1","TEST2")
    # b <- c("\\cite{ready4show2022}", "hjhjhj")
    # tmp <- data.frame(a,b)   
#     kableExtra::kbl(tmp, booktabs = T, escape = F) %>%
#  kableExtra::kable_styling(
#    latex_options = c("striped", "hold_position", "repeat_header")
#    ) %>%  
#   kableExtra::column_spec(2, width = "50em") %>%
# kableExtra::landscape()

checklist_df <- data.frame(Ref = c(paste0("T",1:6),
                                        paste0("I",1:4),
                                        paste0("M",1:2),
                                        paste0("E",1:3),
                                        paste0("L",1:3),
                                        paste0("Y",1:2)),
                           Standard = c("Publicly archived",
                                        "Documented",
                                        "Consistent syntax",
                                        "Literately programmed",
                                        "Code coverage",
                                        "Reproducible",
                                        "Version controlled",
                                        "Semanticly versioned",
                                        "Continuously integrated",
                                        "Deprecation",
                                        "Separate code and data",
                                        "Encapsulated",
                                        "Libraries",
                                        "Inheriting",
                                        "Test data",
                                        "Copyleft code",
                                        "Liberal, safe data terms",
                                        "Citation tools",
                                        "Prediction tools",
                                        "User interface"),
                           Assessment = c("Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "No",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yesg",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "No"),
                           Description = c("5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], <br> 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are permanently archived with unique identifiers.",
                                           "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the package name (e.g. https://ready4-dev.github.io/youthvars). All three Markdown programs are self-documenting, with one [@hamilton_matthew_2022_6129906] including additional instructions in a README file. Only one sub-routine [@matthew_p_hamilton_2022_5976988] is documented with a meaningful README file. All datasets have meaningful metadata descriptors.",
                                           "All libraries, programs and sub-routines use the same house style, which allows most library documentation to be written by algorithms from the ready4fun package [@ready4fun2022]. All libraries except [@matthew_p_hamilton_2021_5646669] use framework syntax, as does one program [@hamilton_matthew_2022_6129906].",
                                           "All programs use literate programming.",
                                           "No current reporting of code coverage.",
                                           "All parts of the study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced (if granted access to source data) or replicated (using supplied synthetic data) with one program [@hamilton_matthew_2022_6129906].",
                                           "All code is version controlled using Git and GitHub. All source code is available in a GitHub organisation [@ready4gh2022].",
                                           "Semantic version is used in all code. As no code library has yet been submitted to CRAN, only the development version extensions of each version number have been incremented to date.",
                                           "All six libraries use continuous integration (CI). CI results for each library can be viewed at a URL that concatenates 'https://github.com/ready4-dev/', the package name and '/actions' (e.g. https://github.com/ready4-dev/youthvars/actions)",
                                           "Retired code is deprecated using lifecycle package tools (e.g. everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ). Package vignettes and datasets are also deprecated e.g. https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )",
                                           "All development code is stored on repos in a GitHub organisation [@ready4gh2022] and all archived releases are available in a Zenodo community [@ready4zen2022]. All non-confidential data is stored in repositories within a Harvard Dataverse collection [@ready4dv2022]. ",
                                           "Four [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155] out of five libraries include encapsulated  modules. Examples are the items beginning with Scorz, Specific and Youthvars that are listed in this table: https://ready4-dev.github.io/ready4/articles/V_01.html#current-ready4-framework-modules as well as the S4 classess from the TTU package listed here: https://ready4-dev.github.io/TTU/reference/index.html ",
                                           "All code libraries include functions. The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above).",
                                           "All modules (see item M2) inherit from the Ready4Module class and can be inherited from.",
                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021]. One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset. The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures and was created to demonstrate generalised applications of study algorithms.",
                                           "All code libraries, programs and sub-routines use GPL-3 licenses. ",
                                           "Datasets use amended version of template provided by Harvard Dataverse [@sampleterms2022].",
                                           "All libraries have CITATION file in inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata.",
                                           "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') are available in the study results dataset [@DVN/DKDIB0_2021] and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data). The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applyihg models compatible with different types of input data. An example program to demonstrate this functionality is available in both RMarkdown [@hamilton_matthew_2022_6416330] and rendered PDF formats (the 'Application.pdf' file in the study results dataset [@DVN/DKDIB0_2021]).  ",
                                           "No Shiny app user interface has yet been developed."))

tb2_nms_chr<-colnames(checklist_df)
checklist_df <- data.frame(checklist_df[,1],
                 rep("&nbsp; ",nrow(checklist_df)),
                 checklist_df[,2],
                 rep("&nbsp; &nbsp; &nbsp; &nbsp; ",nrow(checklist_df)),
                 checklist_df[,3],
                 rep("&nbsp; ",nrow(checklist_df)),
                 checklist_df[,4])
colnames(checklist_df) <- c(" "," ","Standard",#
                             "   ","Met?","   ",
                            tb2_nms_chr[4])
if(params$X@outp_formats_chr[1] == "Word") {
  checklist_df %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL)
  }else{
    checklist_df %>%
    kableExtra::kbl(format = "markdown",
                    booktabs = T,
                    caption = knitr::opts_current$get("tab.cap")) 
    }
```

>>>>

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r cpkgs, tab.cap='Modelling toolkit R packages for developing and using MOSHEMs that meet framework standards', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra)  
df <- tibble::tibble(Package = c("ready4",
                                       "ready4fun",
                                       "ready4class",
                                       "ready4pack",
                                       "ready4use",
                                       "ready4show"),
                           # Version = Package %>%
                           #   purrr::map_chr(~utils::packageDescription(.x) %>%
                           #                    purrr::pluck("Version")),
                           Focus = c("Foundation",
                                     "Module algorithms",
                                     "Module structures",
                                     "Module libraries",
                                     "Datasets",
                                     "Analyses"),
                           A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
                           R = c("4","5","4-5","1,3,6","3,7",""),
                           U = c("","","","1-3","1",""),
                           # E = c("", "1","1-2","1","3",""),
                           # L = c("","","","1,3","2-3",""),
                           # Y = c("","","","","","1-2"),
                           `Depends on` = Package %>%
                             purrr::map(~ {
                               utils::packageDescription(.x) %>%
                                 `[`(c("Depends", "Imports")) %>%
                                 purrr::map(~{
                                   if(is.null(.x)){
                                     character(0)
                                     }else{
                                       .x %>%
                                         strsplit(",\\n") %>%
                                         purrr::flatten_chr() %>%
                                         purrr::map(~strsplit(.x,", ") %>%
                                                      purrr::flatten_chr()) %>%
                                         purrr::flatten_chr() %>% sort() %>%
                                         purrr::discard(~startsWith(.x,"R "))
                                       }
                                   }) %>%
                                 purrr::flatten_chr() %>%
                                 unique() %>%
                                 sort() %>%
                                 purrr::map_chr(~{
                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                                     unname()
                                   if(!is.na(problem_idx_1L_chr))
                                     updated_1L_chr <- updated_1L_chr %>%
                                     stringr::str_sub(end = problem_idx_1L_chr-1)
                                   updated_1L_chr %>% 
                                     trimws(which = "left") 
                                   })
                               }) %>% 
                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
  as.data.frame() 
    df$Ref <- c("@ready42022",
                    "@ready4fun2022",
                    "@ready4class2022",
                    "@ready4pack2022",
                    "@ready4use2022",
                    "@ready4show2022")
df <- df %>%
  dplyr::mutate(Standard = purrr::pmap_chr(df,
                                           ~paste0("A",
                                                  ..3,
                                                  paste0(rep("&nbsp;",
                                                      2+max(nchar(df[,3]))-nchar(..3)),
                                                      collapse = ""#
                                                      ),
                                                  ifelse(..4=="","","R"),
                                                  ..4,
                                                  paste0(rep("&nbsp;",
                                                      2+max(nchar(df[,4]))-nchar(..4)),
                                                      collapse = ""#
                                                      ),
                                                  ifelse(..5=="","","U"),
                                                  ..5,
                                                  paste0(rep("&nbsp;",
                                                      1+max(nchar(df[,5]))-nchar(..5)),
                                                      collapse = ""#
                                                      )#,
                                                  # ifelse(..6=="","","E"),
                                                  # ..6,
                                                  # paste0(rep("&nbsp;",
                                                  #     1+max(nchar(df[,6]))-nchar(..6)),
                                                  #     collapse = ""#
                                                  #     ),
                                                  # ifelse(..7=="","","L"),
                                                  # ..7,
                                                  # # paste0(rep("&nbsp;",
                                                  # #     1+max(nchar(df[,7]))-nchar(..7)),
                                                  # #     collapse = ""#
                                                  # #     ),
                                                  # ifelse(..8=="","","&nbsp; &nbsp; &nbsp; &nbsp; Y"),
                                                  # ..8,
                                                  # paste0(rep("&nbsp;",
                                                  #     1+max(nchar(df[,8]))-nchar(..8)),
                                                  #     collapse = ""#
                                                  #     )
                                                  ))) %>%

  dplyr::select(Package,
                Ref,
                Focus,
                Standard,
                `Depends on`)

names_chr <- names(df)
df <- data.frame(df[,1],
                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
                     nrow(df)),
                 df[,2:3],
                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
                     ,nrow(df)),
                 df[,4],
                 #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
                 df[,5])
colnames(df) <- c("Package",
                  ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
                  "Ref", "Focus", 
                  ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
                  "Standard     ",# " ",
                  "Depends on these R libraries")
#df$Package <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df[,c(1,3:4,6:7)] %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    df$Ref<-NULL
    #df$Package <- ""
    df$Package  <- df$Package %>% 
                      purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
    # df$Package <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
    df[,c(1,3,5:6)]   %>%
    # kableExtra::kbl(format = "markdown",
    #                   escape = F,
    #                 caption = knitr::opts_current$get("tab.cap"))
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(3,latex_valign = "m") %>%
      # kableExtra::column_spec(1, 
      #                         image = kableExtra::spec_image(rep("../Data/images/ready4.png",nrow(df)), 
      #                                                           150, 150)) %>%
      kableExtra::column_spec(4, width = "24em",latex_valign = "m")
    }
```

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
working on discussion

                                        "Semanticly versioned",

@@

                           Description = c("Development and archived code for 5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are available. See https://www.ready4-dev.com/docs/getting-started/software/libraries/types/module/ (for libraries), https://www.ready4-dev.com/docs/getting-started/software/executables/programs/ (for programs) and https://www.ready4-dev.com/docs/getting-started/software/executables/subroutines/",
                                           "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the package name (e.g. https://ready4-dev.github.io/youthvars). All three Markdown programs are self-documenting, with one [@hamilton_matthew_2022_6129906] including additional instructions in a README file. Only one sub-routine [@matthew_p_hamilton_2022_5976988] is documented with a meaningful README file. All datasets have meaningful metadata descriptors.",
                                           "All libraries, programs and sub-routines use the same house style, which allows most library documentation to be written by algorithms from the ready4fun package [@ready4fun2022]. All libraries except [@matthew_p_hamilton_2021_5646669] use framework syntax, as does one program [@hamilton_matthew_2022_6129906].",

@@

                                           "All libraries have a CITATION file in  the inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata.",

@@

                                           "All code libraries include functions. The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above)",
                                           "All module data-structures and algorithms are distributed as code libraries",

@@

                                           "No Shiny app user interface has yet been developed.",

@@

                                           "Semantic version is used in all code. As no code library has yet been submitted to CRAN, only the development version extensions of each version number have been incremented to date.",
                                           "All six libraries use continuous integration (CI). CI results for each library can be viewed at a URL that concatenates 'https://github.com/ready4-dev/', the package name and '/actions' (e.g. https://github.com/ready4-dev/youthvars/actions)",
                                           "Retired code is deprecated using lifecycle package tools (e.g. everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ). Package vignettes and datasets are also deprecated e.g. https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )"

>>>>

                                        "Semantic versioning",

@@

                           Description = c("Datasets are available at https://doi.org/10.7910/DVN/DKDIB0 and https://doi.org/10.7910/DVN/HJXYKQ. For details of where to find Development and Archive code see: https://www.ready4-dev.com/docs/getting-started/software/libraries/types/module/  https://www.ready4-dev.com/docs/getting-started/software/executables/programs/  https://www.ready4-dev.com/docs/getting-started/software/executables/subroutines/ ",
                                           "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the library name (e.g. https://ready4-dev.github.io/youthvars). All three Markdown programs are self-documenting, with one [@hamilton_matthew_2022_6129906] including additional instructions in a README file. Only one sub-routine [@matthew_p_hamilton_2022_5976988] is documented with a meaningful README file. All datasets have meaningful metadata descriptors.",
                                           "All libraries are authored with ready4pack [@ready4pack2022] to ensure a consistent house style. All libraries except [@matthew_p_hamilton_2021_5646669] use framework syntax, as does one program [@hamilton_matthew_2022_6129906].",

@@

                                           "All libraries can return citation details when running R's 'citation' function. All code and data repositories have tools to generate citation details.",

@@

                                           "All code libraries include functions. The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item A2 above)",
                                           "All module data-structures and algorithms are distributed as code libraries.",

@@

                                           "No user interface has yet been developed.",

@@

                                           "Semantic versioning is used in all code. As no code library has yet been submitted to CRAN, only the development version extensions of each version number have been incremented to date.",
                                           "All six libraries use continuous integration (CI). CI results for each library can be viewed at a URL that concatenates 'https://github.com/ready4-dev/', the library name and '/actions' (e.g. https://github.com/ready4-dev/youthvars/actions)",
                                           "Retired code is deprecated using tools from the lifecycle R library (e.g. everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ). Package vignettes and datasets are also deprecated e.g. https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )"
